Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-09 paper/paper.tex
Updates to paper.tex
- Make bibliography smaller
- remove unneeded loading of xypic
- fix PDF metadata
- update list of keywords
- add things to bibliography

\usepackage[usenames]{color}
\usepackage[numbers]{natbib}
\definecolor{citationcolour}{rgb}{0,0.4,0.2}
\definecolor{linkcolour}{rgb}{0,0,0.8}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
            urlcolor=linkcolour,
            linkcolor=linkcolour,
            citecolor=citationcolour,
            pdftitle=Relational Parametricity for Algebraically-Indexed Types,
            pdfauthor={Robert Atkey, Neil Ghani, Patricia Johann, Andrew Kennedy},
            pdfkeywords={}}  
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}
\def\subsubsectionautorefname{Section}

@@

\usepackage{mathpartir}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage[all]{xy}

@@

\keywords
  parametricity, units of measure, dimensional analysis, invariance, computational geometry

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{section-introduction.tex}
\input{geometry-twocolumn.tex}
\input{section-general-framework.tex}
\input{section-instantiations.tex}
\input{section-info-flow.tex}
\input{section-monoid.tex}
\input{section-singleton.tex}
\input{section-metric.tex}
\input{section-discussion.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{abbrvnat}
\bibliography{paper}

\newpage
\appendix

\input{appendix-proofs.tex}

>>>>

\usepackage[usenames]{color}
\definecolor{citationcolour}{rgb}{0,0.4,0.2}
\definecolor{linkcolour}{rgb}{0,0,0.8}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
            urlcolor=linkcolour,
            linkcolor=linkcolour,
            citecolor=citationcolour,
            pdftitle=Relational Parametricity for Algebraically-Indexed Types,
            pdfauthor={Robert Atkey, Patricia Johann, Andrew Kennedy},
            pdfkeywords={}}  
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}
\def\subsubsectionautorefname{Section}

@@

\usepackage{mathpartir}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}

@@

\keywords parametricity, units of measure, dimensional analysis,
invariance, computational geometry, information flow, metric types, uniform continuity

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{section-introduction.tex}
\input{geometry-twocolumn.tex}
\input{section-general-framework.tex}
\input{section-instantiations.tex}
\input{section-monoid.tex}
\input{section-info-flow.tex}
%\input{section-singleton.tex}
\input{section-metric.tex}
\input{section-discussion.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{12}
\softraggedright

\bibitem{abadi99core} 
M. Abadi, A. Banerjee, N. Heintze, and J. G. Riecke. A Core Calculus
of Dependency. Proceedings, Symposium on Principles of Programming
Languages, pp.147-160, 1999.

\bibitem{syntaxforfree}
R. Atkey.  Syntax for Free: Representing Syntax with Binding Using
Parametricity.  Proceedings, Typed Lambda Calculi and Applications,
pp. 35-49, 2009.

\bibitem{TypedSyntax}
N.~Benton, C.-K.~Hur, A.~J.~Kennedy, C.~McBride.
Strongly Typed Term Representations in {Coq}.
{\em Journal of Automated Reasoning} 49(2), pp. 141-159, 2012.

\bibitem{benton06reading}
N.~Benton, A.~Kennedy, M.~Hofmann, L.~Beringer.
Reading, Writing and Relations.
Proceedings, Asian Symposium on Programming Languages and Systems,
pp. 114-130, 2006

\bibitem{bernardy12proofs} 
J.-P.~Bernardy, P.~Jansson, R.~Paterson.
Proofs for free: Parametricity for dependent types.
{\em Journal of Functional Programming} 22(02), pp. 107-152, 2012.

\bibitem{CGAL}
Computational Geometry Algorithms Library (CGAL): User and Reference
Manual.  Available at {\tt http://www.cgal.org}.

\bibitem{chaudhuri10continuity}
S. Chaudhuri, S. Gulwani, and R. Lublinerman.  Continuity Analysis of
Programs.  Proceedings, Symposium on Principles of Programming
Languages, pp. 57-70, 2010.

\bibitem{gallier11geometric}
J. Gallier. {\em Geometric Methods and Applications, For Computer
Science and Engineering. Springer Science+Business Media, LLC}, 2011.

\bibitem{harrison09without}
J.~Harrison.
Without Loss of Generality.
Proceedings, Theorem Proving in Higher Order Logics,
pp. 43-59, 2009

\bibitem{hofmann08correctness}
M. Hofmann. Correctness of effect-based program
transformations. Formal Logical Methods for System Security and
Correctness, pp. 149-173, 2008

\bibitem{jones95functional}
M. P. Jones.  Functional Programming with Overloading and Higher-Order
Polymorphism. Proceedings, Advanced Functional Programming,
pp. 97-136, 1995.

\bibitem{kennedy97relational} 
A. Kennedy. Relational Parametricity and Units of Measure.
Proceedings, Symposium on Principles of Programming Languages,
pp. 442-455, 1997.

\bibitem{CFGADT}
S.~Mann, N.~Litke, T.~DeRose.  A Coordinate Free Geometry {ADT}.
Technical Report CS-97-15, University of Waterloo, 1997.

\bibitem{PittsAM:parpoe}
A. M. Pitts.  Parametric Polymorphism and Operational Equivalence.
{\em Mathematical Structures in Computer Science} 10, pp. 321-359,
2000.

\bibitem{reed10distance}
J. Reed and B. C. Pierce.  Distance Makes the Types Grow Stronger.
Proceeding, International Conference on Functional Programming,
pp. 157-169, 2010.

\bibitem{reynolds83types}
J. C. Reynolds. Types, Abstraction and Parametric Polymorphism.
{\em Information Processing} 83, pp. 513-523, 1983.

\bibitem{sabelfeld01per} 
A. Sabelfeld and D. Sands.  A Per Model of Secure Information Flow in
Sequential Programs.  {\em Higher-Order and Symbolic Computation} 14
(1), pp. 59-91, 2001.

\bibitem{tse04translating}
S. Tse and S. Zdancewic.  Translating Dependency into Parametricity.
Proceedings, International Conference on Functional Programming pp.
115-125, 2004.

\bibitem{wadler89theorems}
P. Wadler.  Theorems for Free!.  Proceedings, International Conference
on Functional Programming Languages and Computer Architecture,
pp. 347-359, 1989.

\end{thebibliography}

%\bibliographystyle{plainnat}
%\renewcommand{\bibfont}{\normalsize}
%\bibliography{paper}

% \newpage
% \appendix

% \input{appendix-proofs.tex}
